\documentclass{letter}

\usepackage[margin=1.5in,headheight=0pt,headsep=0pt]{geometry}
\addtolength{\topmargin}{-35pt}
\addtolength{\textheight}{90pt}

\usepackage{palatino}
\usepackage[super]{nth}

\title{coverletter-medical-receptionist}

\newcommand{\jobtitle}{a Clerical Support Specialist}
\newcommand{\company}{Olympia Orthopedic Associates}

\address{Colton Grainger \\ 1127 Hammock St \\ Houston, TX 77009}
\signature{Colton Grainger}
\begin{document}

\begin{letter}{Olympia Orthopedic Associates, PLLC \\ 2421 Heritage Court SW \\ Second Floor \\ Olympia, WA 98502}
\opening{Dear Sir or Madam:}

I aim to gain employment as \jobtitle\ starting July 24, 2017.

I have performed clerical work since 2015, when I was hired as a grading assistant. I found that, by taking a share of my supervisor's clerical responsibilities, I gave her more time to focus on research and curriculum design.  

In 2016 I graduated with a B.S. in Mathematics-Physics. Shortly after, I committed to a year of service in the Episcopal Service Corps. I am fulfilling this commitment by working as a clerk at the YMCA International Services, a refugee resettlement agency in Houston, TX. %My completion date in the Service Corps is July 15, 2017. %I plan to begin in a professional position in Olympia, WA by July \nth{24}.

At the YMCA, I work on small team to support refugees with complex medical conditions. I balance clerical duties with direct case management. I directly serve 40 clients monthly---arranging medical appointments, transportation and interpretation. %I am also responsible for low-income healthcare applications. %In emergency situations, I accompany clients to safety net services. 
As a clerk, I maintain 240 client case files---with medical records, financial eligibility information, and immigration documents---for 7 staff across 2 departments of the resettlement agency. 

In contributing to the workflow at \company, I anticipate that I will
\begin{itemize}
	\item operate a multi-line phone and receive clients in the office;
	\item handle referrals, schedule appointments, and coordinate with providers;
	\item maintain physical/electronic records and sort sensitive mail; 
%	\item draft, revise, and submit insurance claims as needed; and
	\item develop macros to manage client data and automate repetitive tasks; and 
	\item actively respond to client inquires regarding scheduling and billing.
\end{itemize}
As these responsibilities mirror those I have already taken on, I am confident that I can increase the office's administrative capacity from my start date.

Outside of my professional interests, I am passionate about cycling, hiking, and computer science. I have ambition to pursue graduate studies in Mathematics and, eventually, publish research in support of environmental preservation. 

\closing{Respectfully,}
\ps
\emph{P.S.\ I am available via email, by phone after 3:00 P.M.\ PST, or by scheduled video-chat.}

\end{letter}
\end{document}