\documentclass[margin]{res} 
\setlength{\textwidth}{5.1in}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{fontawesome}
\usepackage{fontspec} 
\setmainfont{Georgia}

\title{cv-uu}

\newcommand\textbox[1]{\parbox{.333\textwidth}{#1} } 
\newcommand\job[3]{\textbf{#1}\hfill {#2}\\ \emph{#3} } 
\newcommand\degree[3]{\textbf{#1}\hfill {#2}\\ \emph{#3} } 
\newcommand\cs[1]{\textsl{#1} } \newcommand\ri[1]{\textsl{#1} }
\newenvironment{details}{\begin{itemize}[itemsep=0.6pt,topsep=2.3pt] }{\end{itemize} } 

\begin{document} 

\noindent\textbox{{\it Curriculum Vitae }\hfill } \textbox{\hfill{\large\bf Colton Grainger}\hfill }

\vspace{-20pt}
\rule{\textwidth}{1pt}

\vspace{-20pt}
\begin{flushright} 
(208)~585-7373\\ coltoncgrainger@gmail.com\\ \faTwitter\ \faGithub\hspace{1ex} {\tt @ColtonGrainger} 
\end{flushright}
\vspace{-24pt}

\begin{resume}

\section{OBJECTIVE}
To complete an M.A. in Mathematics (with applied emphasis) at University of Utah.

\section{EDUCATION}
\degree{B.S. in Mathematics-Physics}{May 2016}{The College of Idaho, Caldwell, ID \hfill {\rm GPA: 3.49}}
    \begin{details}
   		\item Senior Study: \emph{Galois Theory for Differential Equations}
        \item Advised by Dr. Jonny Comes.
    \end{details}

\section{RESEARCH INTERESTS}
\ri{Multiscale Analysis and Computations} for fluid dynamics and ground water flow.\\
\ri{Material Science} concerning percolation models and inverse problems.

\section{EXPERIENCE}
\job{Refugee Medical Care Intern}{August 2016 -- Present}{YMCA International Services, Houston, TX}
    \begin{details}
	  	\item Managed 60 refugee medical cases in a team of 3 staff.
        \item Scheduled medical appointments, transportation and interpretation.
        \item Advocated for clients at clinics, food pantries and emergency shelters. 
	\end{details}
     
\job{Course Grader \& Tutor}{September 2015 -- December 2015}{The College of Idaho}
	\begin{details}
        \item Graded weekly assignments for a section of 25 general physics students.
        \item Tutored 5 calculus students in weekly one-on-one sessions.
    \end{details}
              
\job{Dishwasher \& Server}{Summers 2011 -- 2013, Fall 2015}{The Griddle, Meridian, ID}
    \begin{details}
        \item Served food and kept clean a 100 $\mathrm{m}^2$ commercial kitchen.
    \end{details}    
   
\section{COMMUNITY INVOLVEMENT}
\job{Service Corps Fellow}{August 2016 -- Present}{Texas Episcopal Service Corps, Houston, TX}
	\begin{details}
    	\item Lived in an intentional community with 2 other fellows.
    	\item Committed to 1,700 hours of service in 11 months.
	\end{details}
            
\job{WWOOF Ranch-Hand}{Summer 2016}{Sonnwendhof Biofarm, M\"{o}ckm\"{u}hl, Deutschland}
    	\begin{details}
    		\item Built relationships with American, German and Italian WWOOFers.
            \item Pastured sheep and planted a sustainable garden.
     	\end{details}
            
\section{SKILLS\\(rated out of 5)}
\vspace{0pt}
\begin{multicols}{2}
	\parskip=0pt
    \cs{Spoken Languages}
    		\begin{details}
            	\item \textbf{German} (3), English (5)
        	\end{details}
    \cs{Markup Languages} 
        	\begin{details}
            	\item \textbf{\LaTeX} (4), HTML (2)
            \end{details}
    \cs{Programming}
        	\begin{details}
            	\item \textbf{Python} (3), C++ (2)
            \end{details}
    \cs{Operating}
        	\begin{details}
            	\item \textbf{GNU} (3), Mac (5), Windows (5)
            \end{details}    
\end{multicols}

\section{HONORS}
\vspace{10pt}
	\begin{description}[noitemsep,topsep=0pt]
		\item[Heritage Scholarship] for academic merit \hfill 2012 -- 2016
    	\item[Top Putnam Score] among College of Idaho students \hfill 2013, 2015
        \item[Varsity Skier] on The College of Idaho Ski Team \hfill 2014, 2016
	\end{description}

\end{resume}
\end{document}
