\documentclass[margin]{res} 
\usepackage{june-2017-res}

\newcommand{\jobtype}{n}

\newcommand{\jobtitle}{the AmeriCorps Volunteer Coordinator}
\newcommand{\company}{GRuB}

\newcommand\reference[5]{\textbf{#1}\\\emph{#2}\\#5\\#3\\}

\title{grub-resume-2017}

\begin{document} 
\begin{resume}
\printheader

\section{OBJECTIVE}
\objective{To gain employment as \jobtitle, with start date July 24, 2017.}{ltm}
\objective{To gain full-time employment, with start date July 24, 2017.}{g}
\objective{To gain employment as \jobtitle\ at \company.}{n}

\section{SUMMARY OF QUALIFICATIONS} \vspace{7.8pt}
	\begin{details}
		\flit{Administrative expertise from 1 year of service in refugee medical care.}{ns}
		\flit{1 year of administrative experience in refugee case management.}{h}
		\flit{1 year of administrative experience in refugee medical care.}{gm}

		\flit{Prior experience in sustainable gardening and community outreach.}{n}
		\flit{Enthusiasm for food justice, non-profit development, and volunteerism.}{h}
		\flit{2 years' expertise in clerical work and data management.}{ghltm}

		\flit{Working knowledge of medical billing, public benefits, and immigration law.}{l}
		\flit{Working knowledge of indigent healthcare and public benefit programs.}{s}

		\flit{Ability to balance competing administrative tasks.}{lmg}	

		\flit{Ability to prioritize administrative tasks and handle competing demands.}{lt}
	\end{details}

\section{EDUCATION}
	\degree{B.S. in Mathematics-Physics}{May 2016}{The College of Idaho, Caldwell, ID%\hfill {\rm GPA: 3.49}}
	}
		\begin{details}
			\flit{Senior Study: \emph{Galois Theory for Differential Equations}.}{} %\item Advised by Dr. Jonny Comes.
			\flit{Minors: History, English Literature and German Language.}{ltsg}
			\flit{Prepared technical reports (2 in epidemiology, 1 in mathematics).}{} %HIV in Houston, the Ebola Outbreak in West Africa, Galois theory for differential equations
		\end{details}

\section{PROFESSIONAL EXPERIENCE}
	\job{Clerk | Refugee Medical Care}{September 2016 -- July 2017}{YMCA International Services, Houston, TX}{ltmsefnhg}
		\begin{details}
			\flit{Supported 7 staff over 240 client cases (60 medical, 180 social adjustment).}{nlshgm}
			\flit{Obtained low-income healthcare for 30 cases and rental assistance for 5 cases.}{sh}
			\flit{Scheduled medical appointments with transportation and interpretation.}{ltmhg}
			\flit{Trained volunteers to accompany clients to medical appointments.}{sn} 
			\flit{Created a resource network of safety-net service providers.}{nhs}
 %HEALTHCARE Anasthesia, Samson, Raziah, Mhd Sultan, Shabukon, Yaneisy, Maryam, Al Attabi, cuban walk in, Fatimah, Thamer, Omid, Rimsha, Nasira, Marzieh, cuban walk in, cuban walk in, Ammar, Habal, Azi, Khaibar, Mhd Amin, Musaningare, Nada RENTAL: Raziah, Khaibar, Reza, Mhd Rafique, Awut, Jesus 
			% \flit{Catalogued medical records and filed public benefits applications.}{l} 
			% \flit{Maintained an online repository of safety-net services.}{lt} 			
			% \flit{Coordinated billing during policy changes to Refugee Medical Assistance.}{m}
			% \flit{Vetted client data for the implementation of 3 SQL databases.}{m}
			% \flit{Ran statistical analyses on case notes to determine under-served clients.}{}
			%\flit{Vetted data for 400 clients during the implementation of 3 SQL databases.}{} %RMS, RMA portal and eRED. Wrote scripts in excel to clean the data
			% \flit{Maintained CSV records for 4439 clients and physical archives for \texttildelow 7,000.}{} %PC was audited internal, physical records
			% \flit{Author of data management plans for low-income health care applications, medical transportation}{}
		\end{details}
	\job{Grading Assistant}{September 2015 -- December 2015}{The College of Idaho}{ltmshg}
		\begin{details}
			\flit{Corrected weekly assignments for 25 general physics students.}{ltmshg}
			\flit{Corresponded with faculty to ensure objective and accurate grading.}{ltmshg}%did I have any copying cases?
		\end{details} 
	% \job{Dishwasher}{July 2015 -- December 2015}{The Griddle, Meridian, ID}{ef}
	% 	\begin{details}
	% 		\flit{Kept clean a $1100 \mathrm{ft}^2$ commercial kitchen.}{ef}
	% 	\end{details} 
	% \job{Warehouse Associate}{May 2015 -- August 2015}{Lowe's, Nampa, ID}{ef}
	% 	\begin{details}
	% 		\flit{Unloaded $45' \times 8' \times 10'$ shipping trailers daily.}{ef}
	% 		\flit{Stocked items in the store and warehouse.}{}
	% 		\flit{Directed customers to recommended products.}{}
	% 	\end{details} 
	\job{Dishwasher \& Server}{Summers 2012, 2013, Fall 2015}{The Griddle, Meridian, ID}{ltgshn}
		\begin{details}
			\flit{Kept clean a 600 $\mathrm{ft}^2$ commercial kitchen.}{lthgn}
			\flit{Trained new staff for the front of house and kitchen.}{ltshgn}
			% \flit{Waited on, cleared and turned at least 20 tables daily.}{}
			% \flit{Prepared espresso drinks as a Barista.}{}
			% \flit{Cleaned restrooms, swept and mopped 2400 ft2 daily.}{}
		\end{details} 
%	\job{Breakfast Server}{Summers 2012, 2013}{The Griddle, Eagle, ID}{ef}
%		\begin{details}
%			\flit{Waited on, cleared and turned $20$ tables daily.}{}
%			\flit{Prepared espresso drinks as a Barista.}{}
%			\flit{Cleaned restrooms, swept and mopped $2400 \mathrm{ft}^2$ daily.}{}
%			\flit{Trained new staff.}{}
%		\end{details} 
%	\job{Dining Host}{June 2011 -- August 2011}{Mahoney’s Atlantic Bar and Grill, Orleans, MA}{f}
%		\begin{itemize}
%			\flit{Bussed and cleaned tables.}{}
%			\flit{Worked collaboratively with other servers and bussers.}{}
%			\flit{Managed an hour long wait-list.}{}
%		\end{itemize}
\section{COMMUNITY INVOLVEMENT}
	\job{Service Corps Fellow}{August 2016 -- July 2017}{Texas Episcopal Service Corps, Houston, TX}{ltmsefnhg}
		\begin{details}
			\flit{Completed a year of service (1,800 hours) while living in community.}{ltmsefnhg}
			\flit{Participated in professional development and communication training.}{nhgm}
			\flit{Attended colloquia on HIV outreach and refugee resettlement.}{ls}
			\flit{Provided administrative support for the Refugee Health Working Group.}{t}
		\end{details}
	\job{WWOOF Ranch-Hand}{June 2016 -- August 2016}{Sonnwendhof Biofarm, M\"{o}ckm\"{u}hl, Deutschland}{sefn}
		\begin{details}
			\flit{Worked on a cooperative ranch with German, Italian and Albanian youth.}{n}
			\flit{Pastured two herds of sheep and maintained a sustainable garden.}{n}
		\end{details}
%	\job{Mathmatics Tutor}{September 2012 -- May 2016}{The College of Idaho}{}
%		\begin{details}
%			\flit{Tutored 5 calculus students in weekly one-on-one sessions.}{}
%			\flit{Covered subjects from Basic Algebra to Vector Calculus.}{}
%		\end{details}
%	\job{Varsity Skier}{September 2013 -- January 2016}{The College of Idaho}{fe}
%		\begin{details}
%			\flit{During Fall: ten hours of conditioning weekly.}{}
%			\flit{During Winter: forty hours of practice / competition weekly (excluding travel)}{}
%		\end{details}
	\job{Lead Counselor | Gem Boys State}{June 2014 and 2015}{Northwest Nazerene University, Nampa, ID}{ltmsefnhg}
		\begin{details}
			\flit{Hosted a camp on state government with veterans of the American Legion.}{ltmsefnhg}
			\flit{Supervised 100 students and 12 junior counselors on a team of 4 staff.}{ltmsefnhg}
 		\end{details}

\section{JOB RELATED ABILITIES} \vspace{0pt}
	\begin{multicols}{2}
		\parskip=0pt
		\begin{skill}{Social Services}
			\item Conflict resolution
			\item Volunteer coordination
		\end{skill}
		\begin{skill}{Technology}
			\item Excel \& SQL data management
			\item HTML5/CSS web-hosting
		\end{skill}
		\begin{skill}{Communication}
			\item Public speaking
			\item Event planning
		\end{skill}
		\begin{skill}{Personal}
			\item CPR \& First Aid certified
			\item Excellent health
		\end{skill}
	\end{multicols}

%\section{AWARDS} \vspace{10pt}
%	\begin{description}[noitemsep,topsep=0pt]
%		\award{YMCA Volunteer of the Month}{for securing rental assistance. \hfill January 2017}{sef}
%		\award{Top Putnam Score}{among College of Idaho student. \hfill 2013, 2015}{t}
%		\award{Heritage Scholarship}{for academic merit. \hfill 2012 -- 2016}{ltm}
%	\end{description}
\section{REFERENCES} 
		\reference{Shaoli Bhadra}{Refugee Medical Program Coordinator\\YMCA International Services}{office: 713-339-9015 ext.\ 1051}{cell: 704-651-3610}{\texttt{shaoli.bhadra@ymcahouston.org}}
		\parskip=0pt

		\reference{Salimah Shamsuddin}{Refugee Case Management Coordinator\\YMCA International Services}{office: 713-339-9015 ext.\ 1019}{cell: 205-585-0362}{\texttt{salimah.shamsuddin@ymcahouston.org}}
		
		% \reference{Katie Devine}{Assistant Professor of Physics\\The College of Idaho}{office: 208-459-5064}{cell: 507-261-9310}{\texttt{kdevine@collegeofidaho.edu}}
		
		\reference{Nick Puccio}{Houston Director\\Texas Episcopal Service Corps}{office: 713-353-2107}{cell: 713-497-7969}{\texttt{npuccio@epicenter.org}}

\end{resume}
\end{document}