\documentclass[margin]{res} 
\setlength{\textwidth}{5.1in}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{fontawesome}
\usepackage{fontspec} 
\setmainfont{Georgia}

\title{résumé-ymca}

\newcommand\textbox[1]{\parbox{.333\textwidth}{#1} } 
\newcommand\job[3]{\textbf{#1}\hfill {#2}\\ \emph{#3} } 
\newcommand\degree[3]{\textbf{#1}\hfill {#2}\\ \emph{#3} } 
\newcommand\cs[1]{\textsl{#1} } \newcommand\ri[1]{\textsl{#1} }
\newenvironment{details}{\begin{itemize}[itemsep=0.6pt,topsep=2.2pt] }{\end{itemize} } 

\begin{document} 

\noindent\textbox{\emph{R\'esum\'e}\hfill} \textbox{\hfill{\large\bf Colton Grainger}\hfill }

\vspace{-20pt}
\rule{\textwidth}{1pt}

\vspace{-20pt}
\begin{flushright} 
713~339~9015 ext.\ 1080\\ colton.grainger@ymcahouston.org\\ \faTwitter\ \faGithub\hspace{1ex} \texttt{@ColtonGrainger} 
\end{flushright}
\vspace{-24pt}

\begin{resume}

\section{OBJECTIVE}
To gain employment as a Data Analyst under the Regional Refugee Coordinator.

\section{SUMMARY OF QUALIFICATIONS}
\begin{itemize}
    \item worked 7 months as a clerk in refugee case management.
    \item vetted data during the implementation of 3 refugee databases.

\end{itemize}
\section{PUT THESE LATER}
2 years' experience producing techincal reports from markup language
a vision for the implementation and sustained functioning of the ClientTrack

\section{EDUCATION}
\degree{B.S. in Mathematics-Physics}{May 2016}{The College of Idaho, Caldwell, ID \hfill {\rm GPA: 3.49}}
    \begin{details}
        \item Senior Study: \emph{Galois Theory for Differential Equations}
        \item Advised by Dr. Jonny Comes.
    \end{details}

\section{RESEARCH INTERESTS}

\ri{Multiscale Analysis and Computation} to approach complex systems (e.g., aquifers).\\
\ri{Numerical Methods} to model fluid flow and contaminant diffusion in porous media.

\section{EXPERIENCE}
\job{Refugee Medical Care Intern}{August 2016 -- Present}{YMCA International Services, Houston, TX}
    \begin{details}
        \item Managed 60 refugee medical cases in a team of 3 staff.
        \item Arranged medical appointments with transportation and interpretation.
        \item Facilitated access to low-income health-care and affordable housing.
    \end{details}
     
\job{Course Grader \& Tutor}{September 2015 -- December 2015}{The College of Idaho}
    \begin{details}
        \item Graded weekly assignments for a section of 25 general physics students.
        \item Tutored 5 calculus students in weekly one-on-one sessions.
    \end{details} 
   
\section{COMMUNITY INVOLVEMENT}
\job{Service Corps Fellow}{August 2016 -- Present}{Texas Episcopal Service Corps, Houston, TX}
    \begin{details}
        \item Lived in an intentional community with 2 other fellows.
        \item Committed to 1,700 hours of service in 11 months.
    \end{details}
            
\job{WWOOF Ranch-Hand}{Summer 2016}{Sonnwendhof Biofarm, M\"{o}ckm\"{u}hl, Deutschland}
        \begin{details}
            \item Worked on a cooperative ranch with American, German and Italian WWOOFers.
            \item Pastured two herds of sheep and maintained a sustainable garden.
        \end{details}
            
\section{SKILLS\\(rated out of 5)}
\vspace{0pt}
\begin{multicols}{2}
    \parskip=0pt
    \cs{Languages}
            \begin{details}
                \item \textbf{German} (3), English (5)
            \end{details}
    \cs{Computer Algebra} 
            \begin{details}
                \item \textbf{SageMath} (3), Mathematica (2)
            \end{details}
    \cs{Programming}
            \begin{details}
                \item \textbf{Python} (3), C++ (2)
            \end{details}
    \cs{Operating}
            \begin{details}
                \item \textbf{GNU} (3), macOS (4), Windows (4)
            \end{details}    
\end{multicols}

\section{HONORS}
\vspace{10pt}
    \begin{description}[noitemsep,topsep=0pt]
        \item[Heritage Scholarship] for academic merit \hfill 2012 -- 2016
        \item[Top Putnam Score] among College of Idaho students \hfill 2013, 2015
        \item[Varsity Skier] on The College of Idaho Ski Team \hfill 2014, 2016
    \end{description}

\end{resume}
\end{document}