\documentclass{letter}

\usepackage[margin=1.5in,headheight=0pt,headsep=0pt]{geometry}
\addtolength{\topmargin}{-35pt}
\addtolength{\textheight}{90pt}

\usepackage{enumerate}

\usepackage{palatino}
\usepackage[super]{nth}

\title{statement of understanding}

\newcommand{\jobtitle}{an AmeriCorps YIS}
\newcommand{\company}{CYS}

\address{Colton Grainger \\ 1127 Hammock St \\ Houston, TX 77009}
\signature{Colton Grainger}
\begin{document}

\begin{letter}{Community Youth Services \\ 
ATTN: AmeriCorps Youth in Service Program \\
711 State Ave. NE \\
Olympia, WA 98506}
\opening{To Whom It May Concern,}
% write a brief statement about what you know about our program and how you can contribute to our team (write about your interests, skills, passions, talents and/or hobbies

I intend to join \company\ as \jobtitle\ in fulfillment of a desire to (i) live simply and (ii) serve others. I am applying on a referral from Andrea Fercho at the United Way of Thurston County, who mentioned CYS runs an impressive AmeriCorps program.

I discovered \company\ during a search for work in a field related to refugee social services. On July 15, I will complete a year in the Texas Episcopal Service Corps at the YMCA International Services, a resettlement agency in Houston. My goal is to complete a second year in a multi-faceted organization, similar to the YMCA, that supports persons living in poverty or persons at risk of living in poverty.

Getting involved as \jobtitle\ at \company\ would form a continuous link with the administrative work I am presently doing at the YMCA---in terms of supporting client self-sufficiency and coordinating a continuum of care. I appreciate the size of CYS, the range of partner programs (esp.\ Rosie's Place, the YWCA, and the CCBLA), and the responsibilities of each YIS position.

\emph{What I believe I can contribute to CYS:} I have experience in medical case management and HIV outreach. At the YMCA, I directly serve 40 clients monthly---providing cultural orientation, scheduling medical appointments, and arranging transportation. I work with discretion and cultural sensitivity. I have helped clients to obtain rental assistance, public benefits, and low income medical care. I also have a B.S. in Mathematics-Physics and experience tutoring STEM subjects. I am fortunate to have had supportive mentors and hope to be a mentor for others. 

Outside of my vocational pursuits, I am passionate about hiking, computer programming, and blue grass music. I am an avid cyclist and user of public transportation. I am also an advocate for affordable, sustainable and nutritious food. In the long term, I have ambition to pursue higher education in applied mathematics and, eventually, publish research in support of environmental preservation.

\closing{Respectfully,}
\ps
\emph{P.S.\ I am available via email, by phone after 3:00 P.M.\ PST, or by scheduled video-chat.}

\end{letter}
\end{document}