\documentclass[margin]{res} 
\usepackage{grad-app-res}

\begin{document}
\begin{resume}

\printheader

\section{OBJECTIVE}

To complete an PhD in Applied Mathematics at CU Boulder.

\section{EDUCATION}

\degree{B.S. in Mathematics-Physics}{May 2016}{The College of Idaho, Caldwell, ID \hfill {\rm GPA: 3.49}}
    \begin{details}
        \item Senior Study: \emph{Galois Theory for Differential Equations}
        \item Advised by Dr. Jonny Comes.
    \end{details}

\degree{Continuing Education}{May 2018}{University of Idaho, Engineering Outreach}
    \begin{details}
        \item 9 credits: Differential Equations, Probability, Numerical Methods 
        \item See \href{my Jupyter notebooks}{https://nbviewer.jupyter.org/github/coltongrainger/notebooks/tree/master/}. 
    \end{details}

\section{EXPERIENCE}

\job{Volunteer Program Coordinator}{August 2017 -- Present}{Family Support Center, Olympia, WA}
    \begin{details}
        \item{Supervised volunteers, interns, and work-studies at homeless family shelter.}
        \item{Organized service-learning projects and developed \href{http://volunteer.fscss.org}{\texttt{volunteer.fscss.org}}.}
    \end{details}

\job{Clerk in Refugee Medical Care}{September 2016 -- July 2017}{YMCA International Services, Houston, TX}
    \begin{details}
        \item{Supported 7 staff over 240 client cases (60 medical, 180 social adjustment).}
        \item{Wrote data management plans for the implementation of 3 SQL databases.}
        \item{Created safety-net repo: \href{https://github.com/coltongrainger/ymca-resources/}{\texttt{github.com/coltongrainger/ymca-resources/}.}}
    \end{details}

\job{Grading Assistant}{September 2015 -- December 2015}{The College of Idaho}
    \begin{details}
        \item{Corrected weekly assignments for 25 general physics students.}
     \end{details} 

\section{SERVICE}

\job{AmeriCorps VISTA}{August 2017 -- August 2018}{Corporation for National and Community Service}
    \begin{details}
        \item{Stipended position: 1 year at the Family Support Center.}
    \end{details}

\job{Service Corps Fellow}{August 2016 -- July 2017}{Texas Episcopal Service Corps, Houston, TX}
    \begin{details}
        \item{Stipended position: 1,800 hours at the YMCA International Services.}
    \end{details}

% \section{JOB RELATED ABILITIES} \vspace{0pt}
%     \begin{multicols}{2}
%         \parskip=0pt
%         \begin{skill}{Administrative}
%             \item 70 WPM typing rate
%             \item Proofing \& copy-editing
%         \end{skill}
%         \begin{skill}{Technology}
%             \item Excel \& SQL data management
%             \item HTML/CSS web development
%         \end{skill}
%         \begin{skill}{Languages Spoken}
%             \item Native English
%             \item Intermediate German
%         \end{skill}
%         \begin{skill}{Personal}
%             \item CPR \& First Aid certified
%             \item Excellent health
%         \end{skill}
%     \end{multicols}

\section{SKILLS} \vspace{0pt}
\begin{multicols}{2} \parskip=0pt

    \cs{Programming}
    \begin{details}
    \item \textbf{Python}, C++, Visual Basic
    \end{details}
    
    \cs{Operating}
    \begin{details}
    \item \textbf{Debian 8.6}, macOS 10.12
    \end{details}    
        
    \cs{Markup Languages} 
    \begin{details}
    \item \textbf{\LaTeX}, HTML
    \end{details}

    \cs{Spoken Languages}
    \begin{details}
    \item \textbf{German}, English
    \end{details}

\end{multicols}

\section{HONORS} \vspace{10pt}

\begin{description}[noitemsep,topsep=0pt]
        \item[Heritage Scholarship] for academic merit \hfill 2012 -- 2016
    	\item[Top Putnam Score] among College of Idaho students \hfill 2013, 2015
        \item[Varsity Skier] at The College of Idaho \hfill 2014, 2016
\end{description}

\end{resume}
\end{document}
