\documentclass[margin]{res} 
\setlength{\textwidth}{5.1in} 
\usepackage{enumitem} 
\usepackage{multicol} 
\usepackage{fontawesome} 
\usepackage{fontspec} 
\setmainfont{Georgia} 

\title{cv-cu-boulder}

\newcommand\textbox[1]{\parbox{.333\textwidth}{#1} } 
\newcommand\job[3]{\textbf{#1}\hfill {#2}\\ \emph{#3} } 
\newcommand\degree[3]{\textbf{#1}\hfill {#2}\\ \emph{#3} } 
\newcommand\cs[1]{\textsl{#1} } 
\newcommand\ri[1]{\textsl{#1} } 
\newenvironment{details}{\begin{itemize}[itemsep=0.6pt,topsep=2.2pt] }{\end{itemize} }

\begin{document}
\noindent\textbox{{\it Curriculum Vitae }\hfill } \textbox{\hfill{\large\bf Colton Grainger}\hfill }

\vspace{-20pt}
\rule{\textwidth}{1pt}

\vspace{-20pt}
\begin{flushright}
    (208)~585-7373\\ coltoncgrainger@gmail.com\\ \faTwitter\ \faGithub\hspace{1ex} {\tt @ColtonGrainger}
\end{flushright}
\vspace{-24pt}

\begin{resume}

\section{OBJECTIVE}
To complete an M.S. in Applied Mathematics at CU Boulder.

\section{EDUCATION}
\degree{B.S. in Mathematics-Physics}{May 2016}{The College of Idaho, Caldwell, ID \hfill {\rm GPA: 3.49}}
    \begin{details}
   		\item Senior Study: \emph{Galois Theory for Differential Equations}
        \item Advised by Dr. Jonny Comes.
    \end{details}

\section{RESEARCH INTERESTS}
    \ri{Dynamical Systems} for fluvial geomorphology and agricultural science.\\
    \ri{Stochastic Processes} to model contaminant diffusion and evaluate risk.

\section{EXPERIENCE}
	\job{Refugee Medical Care Intern}{August 2016 -- Present}{YMCA International Services, Houston, TX}
    	\begin{details}
	  		\item Managed 60 refugee medical cases in a team of 3 staff.
            \item Scheduled medical appointments, transportation and interpretation.
            \item Advocated for clients at clinics, food pantries and emergency shelters. 
		\end{details}
    \job{Course Grader \& Tutor}{September 2015 -- December 2015}{The College of Idaho}
     	\begin{details}
        	\item Graded weekly assignments for a section of 25 general physics students.
            \item Tutored 5 calculus students in weekly one-on-one sessions.
        \end{details}      
	\job{Dishwasher \& Server}{Summers 2011 -- 2013, Fall 2015}{The Griddle, Meridian, ID}
        \begin{details}
        	\item Served food and kept clean a 100 $\mathrm{m}^2$ commercial kitchen.
        \end{details}    
   
\section{COMMUNITY INVOLVEMENT}
	\job{Service Corps Fellow}{August 2016 -- Present}{Texas Episcopal Service Corps, Houston, TX}
        \begin{details}
            \item Lived in an intentional community with 2 other fellows.
            \item Committed to 1,700 hours of service in 11 months.
        \end{details}   
	\job{WWOOF Ranch-Hand}{Summer 2016}{Sonnwendhof Biofarm, M\"{o}ckm\"{u}hl, Deutschland}
    	\begin{details}
    		\item Built relationships with American, German and Italian WWOOFers.
            \item Pastured sheep and planted a sustainable garden.
     	\end{details}
           
\section{SKILLS}
\vspace{0pt}
\begin{multicols}{2}
	\parskip=0pt
    \cs{Programming}
        	\begin{details}
            	\item \textbf{Python}, C++, Visual Basic
            \end{details}
    \cs{Operating}
        	\begin{details}
            	\item \textbf{Debian 8.6}, macOS 10.12
            \end{details}    \cs{Markup Languages} 
        	\begin{details}
            	\item \textbf{\LaTeX}, HTML
            \end{details}
    \cs{Spoken Languages}
    		\begin{details}
            	\item \textbf{German} (de-2), English (en-N)
        	\end{details}
\end{multicols}

\section{HONORS} 
\vspace{10pt}
	\begin{description}[noitemsep,topsep=0pt]
		\item[Heritage Scholarship] for academic merit \hfill 2012 -- 2016
    	\item[Top Putnam Score] among College of Idaho students \hfill 2013, 2015
        \item[Varsity Skier] on The College of Idaho Ski Team \hfill 2014, 2016
	\end{description}

\end{resume}
\end{document}
