\documentclass[margin]{res} 
\usepackage{may-2017-res}

\newcommand{\jobtype}{s}

\newcommand{\jobtitle}{a Training and Volunteer Coordinator}
\newcommand{\company}{Pierce County Medical Reserve Corps}

\title{parent-resume-2017}

\begin{document} 
\begin{resume}
\printheader

\section{OBJECTIVE}
\objective{To gain employment as \jobtitle, with start date July 24, 2017.}{ltm}
\objective{To fill the AmeriCorps VISTA position as \jobtitle\ in the \company.}{s}

\section{SUMMARY OF QUALIFICATIONS} \vspace{7.8pt}
	\begin{details}
		\flit{1 year of clerical experience in refugee medical care \& case management.}{s}
		\flit{1 year of clerical experience in refugee medical care.}{tm}

		\flit{2 years' expertise in record keeping and data management.}{ltm}

		\flit{Working knowledge of medical billing, public benefits, and immigration law.}{l}
		\flit{Working knowledge of indigent healthcare and public benefit programs.}{s}

		\flit{Calm demeanour and experience answering multiple phone lines.}{lm}	

		\flit{Ability to priorize administrative tasks and handle competing demands.}{lmt}
		\flit{Ability to balance client services and administrative responsibilities.}{s}
	\end{details}

\section{EDUCATION}
	\degree{B.S. in Mathematics-Physics}{May 2016}{The College of Idaho, Caldwell, ID%\hfill {\rm GPA: 3.49}}
	}
		\begin{details}
			\flit{Senior Study: \emph{Galois Theory for Differential Equations}.}{} %\item Advised by Dr. Jonny Comes.
			\flit{Minors: History, English Literature and German Language.}{ltms}
			\flit{Prepared technical reports (2 in epidemiology, 1 in mathematics).}{} %HIV in Houston, the Ebola Outbreak in West Africa, Galois theory for differential equations
		\end{details}

\section{PROFESSIONAL EXPERIENCE}
	\job{Clerk | Refugee Medical Care}{September 2016 -- July 2017}{YMCA International Services, Houston, TX}{ltmsef}
		\begin{details}
			\flit{Managed 240 cases (60 medical, 180 social adjustment) on a team of 8 staff.}{tm}
			\flit{Supported 7 staff over 240 client cases (60 health, 180 social adjustment).}{ls}
			\flit{Scheduled medical appointments and arranged client transportation.}{ltm}
			\flit{Obtained low-income healthcare for 30 cases and rental assistance for 5 cases.}{sm} %HEALTHCARE Anasthesia, Samson, Raziah, Mhd Sultan, Shabukon, Yaneisy, Maryam, Al Attabi, cuban walk in, Fatimah, Thamer, Omid, Rimsha, Nasira, Marzieh, cuban walk in, cuban walk in, Ammar, Habal, Azi, Khaibar, Mhd Amin, Musaningare, Nada RENTAL: Raziah, Khaibar, Reza, Mhd Rafique, Awut, Jesus 
			\flit{Catalogued medical records and filed public benefits applications.}{l} 
			\flit{Maintained an online repository of safety-net services.}{lt} 			
			\flit{Trained volunteers to accompany clients to medical appointments.}{s} 
			\flit{Reconciled medical bills during revisions to Refugee Medical Assistance.}{m}
			\flit{Reached out to safety-net service providers \& maintained resource networks.}{s}
			% \flit{Experience vetting client data during the implementation of 3 SQL databases.}{}
			% \flit{Ran statistical analyses on case notes to determine under-served clients.}{}
			% \flit{Vetted data for \texttildelow 400 clients during the implementation of 3 SQL databases.}{} %RMS, RMA portal and eRED. Wrote scripts in excel to clean the data
			% \flit{Maintained CSV records for 4439 clients and physical archives for \texttildelow 7,000.}{} %PC was audited internal, physical records
			% \flit{Author of data management plans for low-income health care applications, medical transportation}{}
		\end{details}
	\job{Grading Assistant}{September 2015 -- December 2015}{The College of Idaho}{ltms}
		\begin{details}
			\flit{Corrected weekly assignments for 25 general physics students.}{ltms}
			\flit{Corresponded with faculty to ensure objective and accurate grading.}{ltms}%did I have any copying cases?
		\end{details} 
	% \job{Dishwasher}{July 2015 -- December 2015}{The Griddle, Meridian, ID}{ef}
	% 	\begin{details}
	% 		\flit{Kept clean a $1100 \mathrm{ft}^2$ commercial kitchen.}{ef}
	% 	\end{details} 
	% \job{Warehouse Associate}{May 2015 -- August 2015}{Lowe's, Nampa, ID}{ef}
	% 	\begin{details}
	% 		\flit{Unloaded $45' \times 8' \times 10'$ shipping trailers daily.}{ef}
	% 		\flit{Stocked items in the store and warehouse.}{}
	% 		\flit{Directed customers to recommended products.}{}
	% 	\end{details} 
	\job{Dishwasher \& Server}{Summers 2012, 2013, Fall 2015}{The Griddle, Meridian, ID}{ltms}
		\begin{details}
			\flit{Kept clean a 600 $\mathrm{ft}^2$ commercial kitchen.}{ltm}
			\flit{Trained new staff for the front of house and kitchen.}{ltms}
			% \flit{Waited on, cleared and turned at least 20 tables daily.}{}
			% \flit{Prepared espresso drinks as a Barista.}{}
			% \flit{Cleaned restrooms, swept and mopped 2400 ft2 daily.}{}
		\end{details} 
%	\job{Breakfast Server}{Summers 2012, 2013}{The Griddle, Eagle, ID}{ef}
%		\begin{details}
%			\flit{Waited on, cleared and turned $20$ tables daily.}{}
%			\flit{Prepared espresso drinks as a Barista.}{}
%			\flit{Cleaned restrooms, swept and mopped $2400 \mathrm{ft}^2$ daily.}{}
%			\flit{Trained new staff.}{}
%		\end{details} 
%	\job{Dining Host}{June 2011 -- August 2011}{Mahoney’s Atlantic Bar and Grill, Orleans, MA}{f}
%		\begin{itemize}
%			\flit{Bussed and cleaned tables.}{}
%			\flit{Worked collaboratively with other servers and bussers.}{}
%			\flit{Managed an hour long wait-list.}{}
%		\end{itemize}

\section{COMMUNITY INVOLVEMENT}
	\job{Service Corps Fellow}{August 2016 -- July 2017}{Texas Episcopal Service Corps, Houston, TX}{ltmsef}
		\begin{details}
			\flit{Completed a year of service while living in community.}{ltmsef}
			\flit{Received training in non-violent communication.}{ltmef}
			\flit{Attended colloquia on HIV outreach and refugee resettlement.}{lms}
			\flit{Completed 1,700 hours of service in 11 months.}{}
			\flit{Provided administrative support for the Refugee Health Working Group.}{tm}
		\end{details}
%	\job{WWOOF Ranch-Hand}{June 2016 -- August 2016}{Sonnwendhof Biofarm, M\"{o}ckm\"{u}hl, Deutschland}{sef}
%		\begin{details}
%			\flit{Worked on a cooperative ranch with American, German and Italian WWOOFers.}{}
%			\flit{Pastured two herds of sheep and maintained a sustainable garden.}{}
%		\end{details}
%	\job{Mathmatics Tutor}{September 2012 -- May 2016}{The College of Idaho}{}
%		\begin{details}
%			\flit{Tutored 5 calculus students in weekly one-on-one sessions.}{}
%			\flit{Covered subjects from Basic Algebra to Vector Calculus.}{}
%		\end{details}
%	\job{Varsity Skier}{September 2013 -- January 2016}{The College of Idaho}{fe}
%		\begin{details}
%			\flit{During Fall: ten hours of conditioning weekly.}{}
%			\flit{During Winter: forty hours of practice / competition weekly (excluding travel)}{}
%		\end{details}
	\job{Gem Boys State Counselor}{June 2012, 2013, 2014, 2015}{Northwest Nazerene University, Nampa, ID}{mt}
		\begin{details}
			\flit{Hosted a summer camp on state government with the American Legion.}{tm}
			\flit{Coordinated a summer camp on state government (150 students).}{tm}
			\flit{Coordinated at American Gov't summer camp.}{}
			\flit{Taught 150 students judicial and legislative procedures.}{}
			\flit{Facilitated 4 day mock trial tournaments \& 2 day congressional debates.}{}
 		\end{details}

\section{JOB RELATED COMPETENCIES} \vspace{0pt}
	\begin{multicols}{2}
		\parskip=0pt
		\begin{skill}{Volunteer Coordination}
			\item Ability to recruit
			\item Logistical attention
		\end{skill}
		\begin{skill}{Social Services}
			\item Excellent case notes
		\end{skill}
		\begin{skill}{Technology}
			\item Microsoft Office
			\item Google Drive
			\item HTML5 \& CSS
			\item Website hosting
		\end{skill}

	\end{multicols}

\section{AWARDS} \vspace{10pt}
	\begin{description}[noitemsep,topsep=0pt]
		\award{YMCA Volunteer of the Month}{for securing rental assistance. \hfill January 2017}{sef}
		\award{Top Putnam Score}{among College of Idaho student. \hfill 2013, 2015}{t}
		\award{Heritage Scholarship}{for academic merit. \hfill 2012 -- 2016}{ltm}
	\end{description}
 
% \section{REFERENCES}

% Dr. Katie Devine, Supervisor at The College of Idaho
% office:
% personal: (507) 261-9310
% email: kdevine@collegeofidaho.edu

% Dave Brown 
% relation: Kitchen Manager, my supervisor for dish-washing
% restaurant phone: 208-288-1848
% (call between 8am and 3pm CST, ask for Dave Brown, the Kitchen Manager)

% % John Post
% % relation: Assistant Coach for the College of Idaho Ski Team
% % cell phone: 208-890-1331
% % email: jwpost@mac.com

% % Steven Maughan
% % relation: Scholarship Advisor
% % personal phone: 208-459-5853
% % email: smaughan@collegeofidaho.edu
 
% % Megan Dixon
% % relation: Professor
% % work phone: 208-459-5010
% % email: mdixon@collegeofidaho.edu

% Shaoli Bhadra
% relation: Supervisor at YMCA International Services
% work phone: 713 339 9015 ext. 1051
% cell phone: 704 651 3610
% email: shaoli.bhadra@ymcahouston.org

% Salimah Shamsuddin
% relation: Supervisor at YMCA International Services
% work phone: 713 339 9015
% cell phone: 205 585 0362
% email: salimah.shamsuddin@ymcahouston.org

% Nick Puccio
% relation: Service Corps Advisor
% work phone: 713 353 2107
% email: npuccio@epicenter.org

\end{resume}
\end{document}