\documentclass{letter}

\usepackage[margin=1.75in,headheight=0pt,headsep=0pt]{geometry}
\addtolength{\topmargin}{-30pt}
\addtolength{\textheight}{60pt}

\usepackage{palatino}
\usepackage[super]{nth}

\title{coverletter-legal-clerk}
\signature{Colton Grainger}

\newcommand{\jobtitle}{a Legal Assistant}
\newcommand{\company}{Northwest Justice Project}
\newcommand{\shortcompany}{NJP}

\address{Colton Grainger \\ 2219 Bush Ave NW \\ Olympia, WA 98502}
\begin{document}

\begin{letter}{Northwest Justice Project\\ 711 Capitol Way S., Suite 704\\ Olympia, WA 98501}
\opening{Dear Sir or Madam:}

I aim to gain employment as \jobtitle.

I am motivated to join \shortcompany\ because I believe limited English proficiency should not bar individuals from accessing legal services. I believe that \shortcompany\ models effective altruism by removing barriers for persons of various cultural backgrounds. 

I have performed clerical work since 2015, when I was hired as a grading assistant. %By taking a share of her administrative responsibilities, I gave my supervisor more time to focus on research and curriculum design. 
In 2016 I graduated with a B.S. in Mathematics-Physics. Shortly after, I committed to a year of service at the YMCA International Services, a refugee resettlement agency in Houston, TX. 

At the YMCA, I worked on small team to support refugees with complex medical conditions. I balanced clerical duties with direct case management. I supported 40 clients monthly---arranging medical appointments, transportation and interpretation. %I am also responsible for low-income healthcare applications. %In emergency situations, I accompany clients to safety net services. 
Additionally, I maintained 240 client case files---with medical records, financial eligibility information, and immigration documents---for 7 staff across 2 departments. 

At the Family Support Center of South Sound, I have overhauled the homeless shelter's volunteer program---digitizing records and moving the application process online. 

In contributing to an efficient workflow at \company, I anticipate that I will
\begin{itemize}
	\item draft, revise, and copy-edit correspondence \& legal pleadings
	\item receive clients, schedule appointments and handle referrals;
	\item maintain physical/electronic records and sort sensitive mail;
	\item write macros to manage data and streamline administrative work; and
	\item relieve staff of miscellaneous burdens.
\end{itemize}
As these responsibilities mirror those I have already taken on, I am confident that I can increase \shortcompany's administrative capacity from my start date.

Outside of my professional interests, I am passionate about cycling, hiking, and computer science. I have ambition to pursue graduate study in Mathematics and, eventually, publish research in support of environmental preservation. 

\closing{Respectfully,}

\end{letter}
\end{document}