\documentclass{letter}

\usepackage[margin=1.5in,headheight=0pt,headsep=0pt]{geometry}
\addtolength{\topmargin}{-35pt}
\addtolength{\textheight}{90pt}

\usepackage{enumerate}

\usepackage{palatino}
\usepackage[super]{nth}

\title{coverletter-medical-receptionist}

\newcommand{\jobtitle}{the AmeriCorps Volunteer Coordinator}
\newcommand{\company}{GRuB}

\address{Colton Grainger \\ 1127 Hammock St \\ Houston, TX 77009}
\signature{Colton Grainger}
\begin{document}

\begin{letter}{ATTN: Kerensa Mabwa\\2016 Elliott Ave NW\\Olympia, WA 98502}
\opening{Community Engagement Coordinator Mabwa,}

I aim to become employed as \jobtitle\ at \company. I am applying on a referral from Nicole Peters at Nature Nurtures Farm. 

I am qualified for this position because I have (i) administrative expertise in social services and (ii) enthusiasm for permaculture.

\begin{enumerate}[(i)]
	\item Upon graduation in 2016, I committed a year to the Texas Episcopal Service Corps. I work to support refugees with complex medical conditions at the YMCA International Services, a resettlment agency in Houston. I serve 40 clients monthly---arranging medical appointments, transportation and interpretation. I support 7 staff in 2 departments.
	\item Since my childhood, I have cultivated various gardens in Idaho. Last summer, I volunteered on Sonnwendhof Biofarm in Southern Germany. I learned to garden in a new climate, mow with a scythe, and divide labor between my peers. I am continually motivated by what Aldo Leopold calls a ``land ethic," a set of nested responsibilities to my ecosystem and community.  
\end{enumerate}

At the YMCA International Services, an employee is \emph{strong}, if they successfully advocate for their client. \emph{What makes an employee strong at \company?} 

I could hypothesize: grit.

I want to put in hard work at GRuB to gain experience in permaculture. The experience moves me closer to my vocational calling: ecological design through applied mathematics.

I hope to begin a coorespondence.

\closing{Respectfully,}
\ps
\emph{P.S.\ I am available via email, by phone after 3:00 P.M.\ PST, or by scheduled video-chat.}

\end{letter}
\end{document}