\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\newcommand{\look}{}
\newcommand{\like}{\textbf}
\begin{document}

\section*{CU Boulder, MS Applied Mathematics, 12/15/2016}

	My curriculum would include 30 credit hours, 3/5 of which are applied mathematics courses, and a thesis. My first semester would open with the 500 level courses \emph{Modeling in Applied Mathematics} and \emph{Numerical Analysis I} and the 400 level course \emph{Fourier Series and Boundary Value Problems.} 

	I will need to understand the basic concepts of \look{linear algebra}, have knowledge of a \look{programming language} and be familiar with \look{multivariable calculus}, vector analysis, and theorems of Gauss, Green, and Stokes.

	The faculty at CU Boulder enjoy \like{dynamic systems} and nonlinear phenomenon. Assistant Prof.\ Iam Grooms finds mathematical techniques to support atmosphere and \like{ocean science}. As I am interested to study the effects of climate change, I would be thrilled to work with Dr.\ Grooms.

\section*{University of Utah, MA Mathematics, 01/01/2017}

	For this degree, I would complete 30 hours of coursework, write a thesis and demonstrate standard proficiency in the German language. My first semester would begin with the 500 level courses \emph{Intro to Real Analysis} and \emph{Intro to Numerical Analysis}. 

	The prerequisites are similar to those above: familiarity with \look{advanced calculus}, \look{linear algebra} and \look{scientific computation}.

	Utah hosts workgroups in \like{material science} and structural optimization. Associate Prof.\ Yekaterina Epshteyn researches coarse microstructures. Under her guidance, I could examine \like{soils} and \like{sediments}. Prof.\ Elena Cherkaev studies diffusivity in fluid flows. Maybe we could optimize irrigation techniques.

\section*{Washington State University, MS Mathematics, 01/10/2017}

	This professional degree program requires three group projects and culminates in qualifying examinations. The curriculum emphasizes numerical analysis, optimization, simulation, and statistics. 

	Assistant Prof.\ Tom Asaki uses \like{derivative-free optimization} for image processing. His manuscripts combine topological arguments, algorithmic searches and random variables. I’m intrigued! Assistant Prof.\ Hong Dong applies quadratic programming to \like{sustainable agriculture}. His work sounds really cool. I can imagine myself finding a career in the production of sustainable food.

\section*{Oregon State University, MA Mathematics, 01/15/2017}

	Similar to U Utah. At OSU, Prof.\ Enrique A. Thomas develops mathematical models for problems arising in \like{ecology}, oceanography, hydrology and natural resource management. I imagine myself finding a mathematically meaningful career where I could spend time outdoors.
    
\section*{Colorado State University, MS Mathematics, 02/01/2017}

	Similar to CU Boulder. At this CSU, Associate Prof.\ Iuliana Opera specializes in computational \like{fluid dynamics} and hydromagnetism. Maybe we could develop alternative energy sources. Dr.\ Oliver Pinaud studies \like{wave propagation} in random media. His research seems useful for designing scientific equipment. 


\section*{University of New Mexico, MS Mathematics, 02/15/2017}

	Similar to U Utah, but with an emphasis on applications in \like{theoretical physics}. They have an excellent high-performance computer lab for student research. 

\end{document}
