\documentclass{letter}

\usepackage[margin=1.75in,headheight=0pt,headsep=0pt]{geometry}

\usepackage{palatino}
\usepackage[super]{nth}

\title{Nature Nurtures Farm Cover Letter}
\signature{Colton Grainger}

\newcommand{\jobtitle}{Development Associate}
\newcommand{\company}{Nature Nurtures Farm}

\begin{document}

\begin{letter}{Nature Nurtures Farm \\ 2406 Delphi Rd SW \\ Olympia, WA 98512}
\opening{To Whom It May Concern,}

I am enthusiastic to learn more about working as a \jobtitle\ on \company. Presently, I am a member of the Texas Episcopal Service Corps. I work now on a small team to support refugees with complex medical conditions. As my term comes to an end, I aim to begin a second year of service in Olympia. I intend to shift my focus: from migration to ecology, from medical care to mental health. 

Looking at \company's website, I felt called to answer questions from the internship application. I have written a few questions myself.

I have pastured sheep, kept stables for donkeys, and maintained chicken coops, but I have never worked with cattle or horses. \emph{What animals are kept on the Farm?} Since a child, I have worked in various gardens---on hillsides, in raised beds, scrunched between roads and canals. \emph{How is the garden organized? What is grown?} I am familiar with the climate and soil in Idaho (volcanic, drains through the Columbia) and Baden-W\"urttemburg (chalky, drains through the Rhine). \emph{What is the geology underneath Olympia? What is the soil gradient?}

I am a strong candidate for the \jobtitle\ position because I have a year of experience with refugee medical case management in Houston and an enthusiasm to explore the connection between psychology and ecology. At the refugee resettlement agency, an employee is ``strong,'' if they successfully advocate for their client. \emph{What makes a ``strong" staff member at \company?}

I forward this information with hope to begin a correspondence.

% In contributing to  workflow at \company, I anticipate that I will
% \begin{itemize}
% 	\item receive clients, schedule appointments and handle referrals;
% 	\item prepare agendas, meeting minutes, and reminders for office deadlines;
% 	\item draft, revise, and copy-edit documents as needed;
% 	\item maintain physical/electronic records and sort sensitive mail;
% 	\item write macros to manage data and utilize computational solutions; and
% 	\item relieve staff of miscellaneous administrative burdens.
% \end{itemize}
% As these responsibilities mirror those I have already taken on, I am confident that I can increase \company's administrative capacity from my start date.


\closing{Respectfully,}
\ps P.S. Outside of my professional interests, I am passionate about cycling, hiking, and computer science. I have ambition to pursue higher education in mathematics and, eventually, work towards environmental preservation. 

P.P.S. \emph{I am available via email, by phone after 3:00 P.M.\ PST, or by scheduled video-chat.}

\end{letter}
\end{document}