\documentclass{letter}

\usepackage[margin=1.5in,headheight=0pt,headsep=0pt]{geometry}
\addtolength{\topmargin}{-35pt}
\addtolength{\textheight}{90pt}

\usepackage{enumerate}

\usepackage{palatino}
\usepackage[super]{nth}

\title{coverletter-medical-receptionist}

\newcommand{\jobtitle}{the AmeriCorps Youth Advocate}
\newcommand{\company}{Rosie's Place}

\address{Colton Grainger \\ 1127 Hammock St \\ Houston, TX 77009}
\signature{Colton Grainger}
\begin{document}

\begin{letter}{ATTN: Keylee Marineau\\520 Pear St\\Olympia, WA 98501}
\opening{Program Director Marineau,}

I aim to become employed as \jobtitle\ at \company. I am applying on a referral from Andrea Fercho at the United Way of Thurston County. 

I am interested in this position because I have (i) a year of experience in refugee social services and (ii) enthusiasm to work at agency that provides a ``continuum of care'' for at-risk youth.

\begin{enumerate}[(i)]
	\item Upon graduation in 2016, I committed a year to the Texas Episcopal Service Corps. I work to support refugees with complex medical conditions at the YMCA International Services, a resettlment agency in Houston. I directly serve 40 clients monthly---providing cultural orientation, scheduling medical appointments, and coordinating transportation. I support 7 case managers in 2 departments.
	\item I thrive in supportive roles. As a grading assistant, I found that, by taking a share of my supervisor's administrative responsibilities, I gave her more time to focus on curriculum design. As a lead counselor at Boys State, I supported junior counselors and large groups of high schoolers. At the YMCA, I handled referrals to community organizations and healthcare providers, I recruited volunteers to teach our clients to ride the Houston METRO, and I created an online repository of safety-net services.
\end{enumerate}

This week, as I was digging through clothing donations to find the second shoe in a pair of men's size 11's, I realized that I care deeply to commit to a second year of my life to a comprehensive socical service agency. 

Working at the \company\ would form a continuous link with the work I am presently doing at the YMCA---in terms of nuturing self-sufficiency, coordinating wholistic care, and performing community outreach.

%At the YMCA International Services, an employee is \emph{strong}, if they successfully advocate for their client. \emph{What makes an employee strong at \company?} 

I forward this letter with hopes to begin a coorespondence.

\closing{Respectfully,}
\ps
\emph{P.S.\ I am available via email, by phone after 3:00 P.M.\ PST, or by scheduled video-chat.}

\end{letter}
\end{document}