\documentclass{letter}

\usepackage[margin=1.5in,headheight=0pt,headsep=0pt]{geometry}

\usepackage{palatino}
\usepackage[super]{nth}

\title{Nature Nurtures Farm Cover Letter}
\signature{Colton Grainger}

\newcommand{\jobtitle}{Coordinator}
\newcommand{\company}{Hunger-Free Pierce County Collaborative}

\begin{document}

\begin{letter}{Hunger-Free Pierce County Collaborative \\ United Way of Pierce County \\ 1501 Pacific Ave, Suite 400 \\ Tacoma, WA 98402}
\opening{To Whom It May Concern,}

I am enthusiastic to learn more about working as the \jobtitle\ for the \company. Presently, I am a member of the Texas Episcopal Service Corps. I work on a small team to support refugees with complex medical conditions. As my term comes to an end, I aim to begin a second year of service in Olympia. I intend to shift my focus: from medical care to food justice, from direct service to capacity building. 

I am interested in the \company\ because I have volunteered in food banks and outreach kitchens in Boise, San Fransico, and Houston. I also have 3~years of experience in food service, a native competence in organic gardening, and a passion for conscious food culture. Above all, I am motivated to take on new responsibilities in an organization.  

A few questions: (i) What is expected of the \jobtitle? (ii) Where is the position located? (iii) Who supervises the \jobtitle? (iv) At the refugee resettlement agency, an employee is ``strong,'' if they successfully advocate for their client. What makes a ``strong" employee at the United Way? 

As I have a year of administrative experience in refugee case management, I believe I am a qualified candidate for this position. I am motivated to develop the \company's administrative capacity. In the same way that case management leads a client to self sufficiency, I hope contribute to the sustainable future of \company. 

I forward this information with hope to begin a correspondence.

% In contributing to  workflow at \company, I anticipate that I will
% \begin{itemize}
% 	\item receive clients, schedule appointments and handle referrals;
% 	\item prepare agendas, meeting minutes, and reminders for office deadlines;
% 	\item draft, revise, and copy-edit documents as needed;
% 	\item maintain physical/electronic records and sort sensitive mail;
% 	\item write macros to manage data and utilize computational solutions; and
% 	\item relieve staff of miscellaneous administrative burdens.
% \end{itemize}
% As these responsibilities mirror those I have already taken on, I am confident that I can increase \company's administrative capacity from my start date.


\closing{Respectfully,}
\ps P.S. Outside of my professional interests, I am passionate about cycling, hiking, and computer science. I have ambition to pursue higher education in mathematics and, eventually, work towards environmental preservation. 

P.P.S. \emph{I am available via email, by phone after 3:00 P.M.\ PST, or by scheduled video-chat.}

\end{letter}
\end{document}